Extended Data

### 2021-11-17 doc/manuscript/Dow_manuscript_Nature.Rmd
Add spei details

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring tempreatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020]. 
*ADD SOMETHING ON HOW STANDARD PRECIPITAITON EVAPOTRANSPIRATIN INDEX WAS FOUND*!!!!

>>>>

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring tempreatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020; @begueria_standardized_2017]. Linear models were run with 4-, 6-, and 12-month SPEI values of June, July, and August vs April $T_{max}$ to determine if warm spring temperatures lead to greater summer drought stress.
